Kindly Bent to Free Us

### 2019-07-10 kindly/infer/infer.tex
Principality.

We now show that our extended inference algorithm still satisfies the soundness
and completeness properties of HM(X). This is achieved by extending
the original proofs.
%
The first theorem states that our inference algorithm is sound
with respect to the syntax directed type system.

@@

The proofs are given in \cref{appendix:infer}.

>>>>

We now show that our extended inference algorithm still satisfies the soundness
and completeness properties of HM(X). This is achieved by extending
the original proofs from HM(X), which is done in \cref{appendix:infer}.
%
The first theorem states that our inference algorithm is sound
with respect to the syntax directed type system.

@@

Finally, principality is a direct application of completeness to
toplevel programs.

\begin{corollary}[Principality]
  Let $\inferS{\Ctrue}{\E}{e}{\schm}$ a closed typing judgement.\\
  Then $\inferW{\Sv}{(C,\unif)}{\Eflat\E}{e}{\tau}$
  such that:
  \begin{align*}
    (\Ctrue,\schm_o) &= \generalize{C}{\unif\E}{\tau}
    &\entail{&}{\schm_o \preceq \schm}
    % &( C, \schm, \unif) &\leq (C',\schm',\unif')
  \end{align*}

\end{corollary}
